\documentclass[12pt,a4paper]{book}
\title{Pasta Luego}
\date{21 May, 2021}
\author{/u/Lady\_Nuggie}
\usepackage{geometry}
\begin{document}
\maketitle

A tear drops from peaches eye as she sees the beautiful sunlight of the mushroom kingdom once more, she turns to bowser in a moment of fear and bliss, she asks Bowser, the king koopa himself, ``Why... Why did you release me, Bowser..?''. Bowser gets on his knee and looks peach in the eye ``Be free.. The truth will be known in due time, but I'm afraid I'm not the right one to tell you'' he says sadly. 

Peach returns to the mushroom kingdom, her childhood home, it was just as she remembered it, but everything seemed different all at the same time. Peach almost immediately resumed her duties as ruler. She looked through the medical records of the mushroom kingdom. ``1 hospital admission in the entire 6 years i was gone? So i guess its true.. It really was my fault that so many innocent toads were harmed. Of course its my fault.. I screw everything up.'' 

Peach drowned in her own self hatred. She knew her existence endangered her kingdoms people, but her sadness wasnt only a symptom of her carelessness. Peach felt betrayed by Mario's lack of heroic acts, typically Mario would always come to save her from bowser. Truthfully peach often faked her kidnappings. She was scared of the affect she had on the people in her life, so she faked her kidnapping over and over in a desperate attempt to distance herself from those she loved. 

She ranted on and on, ``how could he leave me with bowser! He's supposed to save me, he always saved me, its Mario Jumpman Mario for gods sake, its his damn job to save me''. Peach could rant about Mario all she wanted on the outside, but on the inside she knew it was her fault that Mario didn't rescue her. It was another classic ``toad who cried koopa'' situation, she faked her kidnapping so much that when it really happened, Mario didnt care for her. Peach felt open to fixing her friendship with mario, after all she caused this and mario did nothing wrong. All this kidnapping thought led peach back to a final question. Why bowser would free her? Guilt? Obligation? Was there a princess better than her? 

Peach didn't get to finish her thoughts as a chorus of toads sang out to her from beyond the castle walls. ``oHHhH pEEEAchH yOuuU hAvEE vIsITORs.'' Peach hesitantly peaked the door open. She hated those fungus freaks, but she felt entitled to keep them around due to how much harm shes caused them. The doorway revealed a man she hadn't seen in years.. a tall man, sporting green. It was Luigi Mario, the lean, mean, green, goomba stomping machine she knew as her childhood best friend. 

Luigi placed his hand on Peaches shoulder with a dread filled face of remorse. ``Peach.. i dont know how else to say this. For lack of a better word.. mari- I-I..I don't think I can do this..'' Luigi takes a deep breath, his breathing seems unsteady as if he's hurt deeply. ``Mario's fucking dying''. ``DEAR GOD'' peach screams in a mix of shock and immediate mourning. peach immediately had questions rush through her head. ``Is this why he never saved me?'', ``whats wrong with him?'' ``is this my fault?'' ``Is this why bowser released me?'' Peaches mind wishes she was never freed from bowsers castle, but it doesn't matter, her body is already moving.

With tears in her eyes, peach hastily approaches an old warp pipe to the mushroom kingdom hospital. She rips off the lid and tears out cobwebs. ``This pipe was probably closed off due to the kingdoms lack of medical emergencies since I was kidnapped.'' She crawls into the warp pipe and begins soaring through miles of tunnel submerged under dirt. The smell is absolutely putrid. Ever since the pipe was abandoned, the homeless toad population seems to have been using it as a toilet. In no time peach arrives at the hospital, her dress is drenched in the piss and shit of toads, another reason to hate them.

Peach enters the building. ``They really put mario in here? This place is crumbling as I speak! Nobody has been here in ages.'' Peach continues searching the hospital until a sound stops her in her tracks. The sound of a heartbeat monitor. She walks slowly into the room. ``M- Mario..? Is that you..?'' She asks to the familiar red plumber. Mario looks up, tears in his eyes, ``itsa all over.. ima going to the la big meataball in the sky, peach''. Peach wipes her tears ``Don't talk that way Mario, your gonna be okay''. Mario chuckles ``It's too late peach.. itsa stage 4 le terminal cancer, as ita shockingly turns out, getting upa close with stars isn't too great for your-ah body. Who-ah woulda guessed. look after Luigi for me, okay?'' 

Mario takes one final breath before saying his final words. ``Arrivaderci.. peach''. ``No.. NO! this cant be happening! Your not dead! You cant be!'' She leaps towards Mario's corpse and begins yanking on his mustache hairs. ``You're Mario Jumpman Mario! You don't die!.. You can't.. PLEASE MARIO. Jump up, my superstar...'' Peach reaches for Mario's iconic hat, ``Please wake up...,'' She says as she pulls the hat off, to see Mario's bald head. Peach breaks down on the floor in a fit of tears. In this time Peach is completely and utterly destroyed, not a shred of happiness remains within her soul. Out of desperation and anger, Peach punches the wall, before continuing to cry. Peach was oblivious to the fact that she put a crack in the wall, a crack that's beginning to spread further. 

Suddenly a chunk of the ceiling collapses. Booming thuds of concrete on concrete echo from across the building. The hospital began to collapse, all hope is lost for the princess, or so it seems... Suddenly Luigi Mario, the man, the myth, the legend, jumps towards peach and tackles her to safety moments before the roof collapsed right where she was standing. Luigi looks peach in the eyes, ``escape through the window, peach.. It's your only option.'' Tears begin to well up in peaches eyes once more. ``But what about you, Luigi.. It's not too late, you can escape with me!'' Peach says as the building crumbles further. Luigi grows angry, he fears losing another person important to him. ``JUST LEAVE ALREADY!!'' Peach is terrified at Luigis sudden outburst, but theres more important matters to concern about. 

Peach gets halfway out the window before glancing at Luigi. ``Peach, I can't leave now.. I have to stay beside him, even through deaths gate..''. ``I understand.'' Says peach, before jumping out the window. When peach lands she feels immediate painful regret. What she haven't realized before jumping was that she wouldn't just be leaving behind Luigi, she'd be leaving behind her whole life. She turns back in an attempt to save Luigi, but as she turns towards the window, she sees Luigi huddle over his brothers corpse in a desperate attempt to preserve his body from the weight of the rubble. Luigi sheds a tear, ``I'll see you soon.. Brother..''. 

The buildings last support crumbles and Luigi is crushed by hundreds of pounds of concrete. Peach sits there in horror knowing whatever's left of the men she knew, is unrecognizable. Then it hits her, none of this would have happened if she had just stayed calm. Once again it was peaches fault. Cold and alone, with tear streaked cheeks, peach takes a warp pipe back to the castle, originally she felt sad, but now she felt nothing but emptiness. She tied a rope to the castle's chandelier, before stepping on the head of a toad, in-fact it was the toad, her loyal servant who stayed by her side through everything. Toad didn't seem to understand what was happening. ``Toad, close your eyes, you don't deserve to see this, please take care of the castle.. this isn't your fault.''

With no hesitation peach jumped from the toads head and hanged herself. Soon enough her face went blue and she passed away. However this tragic tale doesn't end here, you see. Luigi successfully protected Mario's body from the rubble. Mario awoke with a strange sensation, and then it hit him, he lost 2 lives in one day, it had been so long since he'd last fought bowsers army that he had forgotten about his supernatural ability to regenerate upon death. ``I've only got-ah singular 1-up-ah left..''

Mario looked into the night sky, alone. He looked down to see dark red spaghetti, ``no ita canta be!'' Mario lifts a chunk of concrete to find a green hat, stained with blood. ``I canta bare to see thisa anymore''. Mario jumps through the warp pipe, as he soars through the pipes, tears fly behind him. He couldn't handle seeing what was left of a person he loved so much. He arrived at the the mushroom kingdom, only to see the absolute worst thing he could see in this moment, peaches corpse, hanging like a spaghetti noodle from a fork, like a string of cheese from a hot pizza, like a strand of drool from his mouth upon seeing a meatball. In that moment marios mind went blank, he knew he had to do. With zero facial expression, mario delicately removed peaches body from the noose, and stuck it around his own neck. Mario shed a single tear and whispered in a broken and saddened voice, "Pasta luego...". Mario double jumped into the air and cut off oxygen to his lungs, as he hung there, he felt no regrets.


\vspace*{\fill}
\centering
\large{The end}
\end{document}

